### 2023-09-17 chapters/introduction.tex
More work on background and introduction

\begin{figure}[t]
    \centering
    \includegraphics[width=0.95\textwidth]{uber_nhsa_accident.png}
    \caption{A pedestrian was killed by an Uber self-driving car in Tempe, Arizona in 2018. The car's sensors detected the pedestrian $5.6$ seconds before the crash, but the self-driving system failed to recognize the uncertainty of multiple object misclassifications and so did not correctly predict her path or reduce the SUV's speed \cite{nationaltransportationsafetyboardnhsa_collision_2019}.}
    % \caption{Aerial view of crash location showing path of pedestrian as she attempted to cross N. Mill Avenue and movement and speed of SUV at three points before impact. Pedestrian's path shows her position from initial detection ($5.6$ seconds before impact) until impact; SUV's position is shown at corresponding times beginning $4.2$ seconds before impact \cite{nationaltransportationsafetyboardnhsa_collision_2019}.}
    \label{fig:uber_nhsa_accident}
\end{figure}

Though this incident is an extreme one, it highlights the challenges of applying machine learning in real-world scenarios and underlines the need for machine learning systems to be robust in rare, adverse or difficult situations.
Recently, European policymakers proposed a set of requirements for applications of machine learning to ensure that they are safe, reliable, and trustworthy \cite{europeancommission_briefing_2021}. This AI Act groups applications of machine learning into three categories based on the potential risk they pose to society: limited risk, high risk, and unacceptable risk. Limited risk applications, for instance within gaming, must meet transparency requirements, and unacceptable risk applications, such as public use of facial recognition, are banned. High risk applications include those in healthcare and must meet a strict set of requirements focusing on anti-discrimination and robustness. 
%
One of the key ways to improve the safety, reliability and trustworthiness of machine learning systems is to equip them with the ability accurately estimate the uncertainty of their predictions. 
A model that can accurately estimate the uncertainty of its predictions is able to communicate to other systems or humans when it is not to be trusted, and so, is able to reduce the risk of wrong predictions leading to catastrophic mistakes. 
Fittingly, a recent study by the European Parliamentary Research Services concluded:

@@

In practice, we are interested in the predictive uncertainty, so we need to include both aleatoric and epistemic uncertainty in the estimate. 
Since sources of epistemic uncertainty are by definition those sources not represented in the data, it is not possible to model them directly, as it is for aleatoric uncertainty. This generally makes epistemic uncertainty more difficult to model and quantify than aleatoric uncertainty. 
Some methods for estimating epistemic uncertainty include Bayesian neural networks \cite{mackay_practical_1992, neal_bayesian_1995}, Monte Carlo dropout \cite{gal_dropout_2016}, and ensembling \cite{lakshminarayanan_simple_2017}. Common to these methods is that they represent epistemic uncertainty by an implicit or explicit distribution over the model parameters. This is in contrast to aleatoric uncertainty, which is usually represented by a distribution over the data. The methods often require multiple forward passes through the model to estimate the predictive uncertainty. This makes them computationally expensive and impractical for real-time applications such as speech recognition.

\section{Thesis scope and outline}
%
% OUTLINE: 
% - Tie together the different topics of the thesis and point briefly to the relevant papers.
%
% The complete set of research published as part of this project covers a number of topics related to decision-support in medical conversations. 
% One group of the primary papers is concerned with generative latent variable models and their applications to estimation of epistemic uncertainty and speech modelling \cite{havtorn_hierarchical_2021,havtorn_benchmarking_2022,bergamin_modelagnostic_2022}. 
% Another group of studies examines self-supervised speech representation learning as an alternative to generative latent variable models \cite{mohamed_selfsupervised_2022,borgholt_brief_2022} and explores them for speech recognition \cite{borgholt_scaling_2021} and spoken language understanding \cite{borgholt_we_2021}. 
% Finally, a group deals with applications of machine learning within the medical domain, including recognition of stroke cases in calls to medical helplines \cite{wenstrup_retrospective_2023} and medical coding of clinical notes \cite{edin_automated_2023}.

This introduction provided a high-level overview of the motivation behind the research project and highlighted important use-cases of speech processing, natural language processing and the importance of uncertainty quantification. The remainder of \cref{part:background} consists of two chapters. \Cref{chp:technical-background} provides relevant technical background to the papers of the thesis, including uncertainty, out-of-distribution detection, and variational autoencoders. Finally, \cref{chp:main-contributions} outlines the main contributions of the thesis in relation to the published papers and the research project as a whole.

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=0.95\textwidth]{uber_nhsa_accident.png}
    \caption{A pedestrian was killed by an Uber self-driving car in Tempe, Arizona in 2018. The car's sensors detected the pedestrian $5.6$ seconds before the crash, but the self-driving system failed to recognize its own uncertainty in multiple object misclassifications and so did not correctly predict her path or reduce the SUV's speed \cite{nationaltransportationsafetyboardnhsa_collision_2019}.}
    % \caption{Aerial view of crash location showing path of pedestrian as she attempted to cross N. Mill Avenue and movement and speed of SUV at three points before impact. Pedestrian's path shows her position from initial detection ($5.6$ seconds before impact) until impact; SUV's position is shown at corresponding times beginning $4.2$ seconds before impact \cite{nationaltransportationsafetyboardnhsa_collision_2019}.}
    \label{fig:uber_nhsa_accident}
\end{figure}

Uber is not the only actor facing the challenges of applying machine learning in real-world scenarios. A recent report by the Washington Post found that Tesla's Autopilot system has been involved in at least 736 crashes in the last four years with 16 fatalities \cite{siddiqui_17_2023}. 
Although recent statistics published by Waymo, the self-driving car company owned by Google's parent company Alphabet, revealed far fewer crashes, with only 2 of 20 incidents over 1 million miles meeting reporting criteria, it is interesting to note that the cars are all operated in the sunny states of California and Arizona, where driving conditions vary relatively little \cite{hawkins_waymo_2023}. 
While driver-assistance systems undoubtedly help reduce accidents in many case, and has great future potential, the issues of current systems highlight the need for machine learning systems to be robust in rare, adverse or difficult situations.

Recently, European policymakers proposed a set of requirements for applications of machine learning to ensure that they are safe, reliable, and trustworthy \cite{europeancommission_briefing_2021}. This AI Act groups applications of machine learning into three categories based on the potential risk they pose to society: limited risk, high risk, and unacceptable risk. Limited risk applications, for instance within gaming, must meet transparency requirements, and unacceptable risk applications, such as public use of facial recognition, are banned. High risk applications include those in healthcare and must meet a strict set of requirements focusing on anti-discrimination and robustness. 
%
One of the key ways to improve the safety, reliability and trustworthiness of machine learning systems is to equip them with the ability accurately estimate the uncertainty of their predictions. 
A model that can accurately estimate the uncertainty of its predictions is able to communicate to other systems or humans when it is not to be trusted, and so, is able to reduce the risk of wrong predictions leading to catastrophic mistakes. 
Fittingly, a recent study by the European Parliamentary Research Services concluded:

@@

In practice, we are interested in the predictive uncertainty, so we need to include both aleatoric and epistemic parts in the uncertainty estimate. 
Since sources of epistemic uncertainty are by definition those not represented in the data, it is not generally possible to model them directly, as it is for aleatoric uncertainty. This makes epistemic uncertainty more difficult to model and quantify than aleatoric uncertainty. 
% Methods for estimating epistemic uncertainty include Bayesian neural networks \cite{mackay_practical_1992, neal_bayesian_1995}, ensembling \cite{gal_dropout_2016,lakshminarayanan_simple_2017} and a suite of recent research into out-of-distribution detection (see \cref{sec:out-of-distribution-detection}). 
In contrast to aleatoric uncertainty, which is usually represented by a distribution over the data, epistemic uncertainty is often represented by an implicit or explicit distribution over the model parameters, such as in Bayesian neural networks \cite{mackay_practical_1992, neal_bayesian_1995} and ensemble models \cite{gal_dropout_2016,lakshminarayanan_simple_2017}. In most cases, such methods require multiple forward passes through the model to estimate the predictive uncertainty making them computationally expensive and impractical for real-time applications. Within the field of out-of-distribution detection, the epistemic uncertainty is not always expressed in model parameters, but sometimes by a distribution over data representations, or output probabilities with special classes for out-of-distribution data. In such cases, the uncertainty can be estimated in a single forward pass through the model.

\section{Thesis scope and outline}
%
% OUTLINE: 
% - Tie together the different topics of the thesis and point briefly to the relevant papers.
%
% The complete set of research published as part of this project covers a number of topics related to decision-support in medical conversations. 
% One group of the primary papers is concerned with generative latent variable models and their applications to estimation of epistemic uncertainty and speech modelling \cite{havtorn_hierarchical_2021,havtorn_benchmarking_2022,bergamin_modelagnostic_2022}. 
% Another group of studies examines self-supervised speech representation learning as an alternative to generative latent variable models \cite{mohamed_selfsupervised_2022,borgholt_brief_2022} and explores them for speech recognition \cite{borgholt_scaling_2021} and spoken language understanding \cite{borgholt_we_2021}. 
% Finally, a group deals with applications of machine learning within the medical domain, including recognition of stroke cases in calls to medical helplines \cite{wenstrup_retrospective_2023} and medical coding of clinical notes \cite{edin_automated_2023}. 
%
This introduction provided a high-level overview of the motivation behind the research project and highlighted important use-cases of speech processing, natural language processing and the importance of uncertainty quantification. The remainder of \cref{part:background} consists of two chapters. \Cref{chp:technical-background} provides relevant technical background to the papers of the thesis, including uncertainty, out-of-distribution detection, and variational autoencoders. Finally, \cref{chp:main-contributions} outlines the main contributions of the thesis in relation to the published papers and the research project as a whole.
